### 2015-02-22 fundamentals/impl.tex
reduces come git flow text that got into the weeds

\Cyclus uses a strategy known as \emph{git flow}
\cite{kalliamvakou_code-centric_2014}
to manage topical branches where individuals develop code: the mainline development
branch (simply known as develop), and the stable branch (called master).
In addition to these rules and delineations, \Cyclus also imposes rules on
when it is acceptable from a quality control standpoint to merge code from
the personal topical branches into the develop branch. All software at this stage
must have sufficient successful tests and comprehensive documentation. Without
these core pieces, proposed changes are not allowed into \Cyclus. As an example, a schematic of
the development stages between reporting a bug and merging the fix is shown in
Figure \ref{fig:gitprocess}.

>>>>

\Cyclus uses a strategy known as \emph{git flow}
\cite{kalliamvakou_code-centric_2014} to manage topical branches where
individuals develop code in parallel and changes are only merged into the
mainline branch after when it is acceptable from a quality control standpoint
All software at this stage must have sufficient successful tests and
comprehensive documentation.  Proposed changes must be sufficiently documented
and tested before they are allowed into \Cyclus.  As an example, a schematic of
the development stages between reporting a bug and merging the fix is shown in
Figure \ref{fig:gitprocess}.
